The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-03-28 ms.Rmd
Escape asterisk that was being counted as a list.

@@

This function meets the minimal requirements of a *covariate* module (see Figure \ref{fig:workflows} Panel B); returning a `Raster*` object of the correct dimensions.

@@

```{r fengworkflow, eval = TRUE}
Feng_Papes <- workflow(occurrence = SpOcc('Dasypus novemcinctus',
                                          extent = c(-130, -20, -60, 60)),
                        covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                            layers = c(1:4, 6, 9, 10, 12, 15)),
                          process = Chain(Clean, # Remove rows w/ impossible, unlikely or missing lat lon.
                                          Background(n = 1000, bias = 200), #background w/in 200km of occurrences
                                          # MESSMask),  # Still to be implemented. mask out areas beyond extremes in train data
                                          Crossvalidate(k = 5)),
                            model = MaxEnt,
                           output = Chain(PerformanceMeasures, PrintMap))

>>>>

```{r knitrOpts, echo = FALSE, cache = FALSE, eval = TRUE}
opts_chunk$set(fig.path = 'figs/')

@@

This function meets the minimal requirements of a *covariate* module (see Figure \ref{fig:workflows} Panel B); returning a `Raster\*` object of the correct dimensions.

@@

```{r fengworkflow, eval = TRUE, results = 'hide', message = FALSE}
Feng_Papes <- workflow(occurrence = SpOcc('Dasypus novemcinctus',
                                          extent = c(-130, -20, -60, 60)),
                        covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                            layers = c(1:4, 6, 9, 10, 12, 15)),
                          process = Chain(Clean, # Remove rows w/ impossible, unlikely or missing lat lon.
                                          Background(n = 1000, bias = 200), #background w/in 200km of occurrences
                                          # MESSMask),  # Still to be implemented. mask out areas beyond extremes in train data
                                          Crossvalidate(k = 5)),
                            model = MaxEnt,
                           output = Chain(PerformanceMeasures, PrintMap))
